---
title: "EDA_Dashboard"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    theme: 
      version: 4
      bootswatch: flatly
runtime: shiny
---

```{r setup, include=FALSE}

thematic::thematic_rmd(font = "auto")
library(flexdashboard)
library(plotly)
library(tidyverse)
library(DT)
library(shiny)
library(dplyr)
```


Intro {data-orientation=rows}
=====================================

{.sidebar data-width=200}
------------------------------------------

```{r}

fileInput("file","Choose CSV file",
          multiple = FALSE,
          accept = c("text/csv",
                     "text/comma-seperated-values,text/plain",
                     ".csv"))

```


Row {data-height=300}
-------------------------------------

### The dataset




```{r}

renderTable({
  
  req(input$file)
  df <- read_csv(input$file$datapath)
  glimpse(df)
  
})

```


Column {.tabset}
------------------------------------

### Distribution of Quantitative Variables

```{r}
library(DT)
renderDataTable({
  req(input$file)
  df <- read_csv(input$file$datapath)
  
  
  library(data.table)
  library(summarytools)

  datatable(round(descr(df),3), fillContainer = T)
  
})

```

### Composition of Qualitative Variables

<style> #dt{ overflow: auto; } </style>   



```{r}
selectInput("Categorical_0","Select the Categorical Variable",choices =c())

observe({
  req(input$file)
  df <- read_csv(input$file$datapath)
  
  
  Categorical_df <- df %>%
    select_if(is.character)
  
  
  Cate <- colnames(Categorical_df)
  
  updateSelectInput(session,"Categorical_0",choices = Cate)
})

```


```{r}

library(DT)
renderDataTable({
  req(input$file)
  df <- read_csv(input$file$datapath)
  
  
  library(data.table)
  library(summarytools)
  

  datatable(round(freq(df[[input$Categorical_0]]),3), fillContainer = T)
  
})


```


Relationship between a Quantitative and a Qualitative variable
=====================================

Column {.sidebar data-width=200}
---------------------------------------

```{r} 

selectInput("Numerical","Select the Numerical Variable",choices =c())
selectInput("Categorical","Select the Categorical Variable",choices =c())

observe({
  req(input$file)
  df <- read_csv(input$file$datapath)
  
  Numerical_df <- df%>% 
    select_if(is.numeric)
  Categorical_df <- df %>%
    select_if(is.character)
  
  Num <- colnames(Numerical_df)
  Cate <- colnames(Categorical_df)
  
  updateSelectInput(session,"Numerical",choices = Num)
  updateSelectInput(session,"Categorical",choices = Cate)
})

```


Column {data-width=650}
-------------------------------------



### Box-Plot

```{r}
renderPlotly({
  req(input$file)
  df <- read_csv(input$file$datapath)
  
   plot_ly(df,
              x = ~df[[input$Numerical]],
              color = ~df[[input$Categorical]],
              colors = "Paired",
              type = "box") %>%
  layout(title = "",
         xaxis = list(title = "" ,
                      zeroline = FALSE))
})
```

Column {data-width=350}
-------------------------------------

### Distribution of the Categorical Variable

```{r}
renderPlotly({
  req(input$file)
  df <- read_csv(input$file$datapath)
  
  df %>%
    count(var = df[[input$Categorical]], name = "count") %>%
    plot_ly( x = ~var, y = ~ count, type = "bar", marker = list(color = '#008ae6',
                           line = list(color = '#008ae6', width = 2)), hoverinfo = "x+y") %>%
    add_text(text = ~paste0( " (",   scales::percent(count/sum(count)),")"), 
           textposition = "bottom", 
           textfont = list(size = 12, color = "white"), 
           showlegend = FALSE) %>%
    layout(xaxis = list(title = ""), yaxis = list(title = ""))
    
})
```


### Distribution of the Numerical Variable

```{r}
renderPlotly({
  req(input$file)
  df <- read_csv(input$file$datapath)
  
  plot_ly(x = df[[input$Numerical]], type = "histogram",  marker = list(color = "#008ae6",
                            line = list(color = "darkgray",
                                        width = 1)))
})
```


Relationship between two Quantiative variables and a Qualitative variable {data-orientation=column}
=====================================


Column {.sidebar data-width=200}
---------------------------------------

```{r}
selectInput("Numerical_1","Select a Numerical Variable for X-axis",choices =c())
selectInput("Numerical_2","Select a Numerical Variable for Y-axis",choices =c())
selectInput("Categorical_1","Select a Categorical Variable",choices =c())


observe({
  req(input$file)
  df <- read_csv(input$file$datapath)
  
  Numerical_df <- df%>% 
    select_if(is.numeric)
  Categorical_df <- df %>%
    select_if(is.character)
  
  Num <- colnames(Numerical_df)
  Cate <- colnames(Categorical_df)
  
  updateSelectInput(session,"Numerical_1",choices = Num)
  updateSelectInput(session,"Numerical_2",choices = Num)
  updateSelectInput(session,"Categorical_1",choices = Cate)
})
```

Column
---------------------------------------
### Correlation between Variables

```{r}

renderPlotly({
  req(input$file)
  df <- read_csv(input$file$datapath)
  
 p <- ggplot(df, aes(x = df[[input$Numerical_1]], y = df[[input$Numerical_2]], fill = df[[input$Categorical_1]])) + 
   xlab ("Numerical_1") +
   ylab ("Numerical_2") + 
  geom_jitter(aes(color = df[[input$Categorical_1]] ))
ggplotly(p)
})
```


Relationship between Two Qualitative Variables
==============================================

Column {.sidebar data-width=200}
---------------------------------------

```{r}


selectInput("Categorical_21","Select a Categorical Variable",choices =c())
selectInput("Categorical_22","Select a Categorical Variable",choices =c())


observe({
  req(input$file)
  df <- read_csv(input$file$datapath)
  
  Numerical_df <- df%>% 
    select_if(is.numeric)
  Categorical_df <- df %>%
    select_if(is.character)
  
  Num <- colnames(Numerical_df)
  Cate <- colnames(Categorical_df)
  

  updateSelectInput(session,"Categorical_21",choices = Cate)
  updateSelectInput(session,"Categorical_22",choices = Cate)
})

```

Column
---------------------

### Mosaic Plot

```{r}
library(ggmosaic)

renderPlotly({
  req(input$file)
  df <- read_csv(input$file$datapath)

  

  print(input$Categorical_21)
  print(input$Categorical_22)
  
  
q <- ggplot(df ) +
  geom_mosaic(aes(x = product(!!sym(input$Categorical_21), !!sym(input$Categorical_22)), fill=!!sym(input$Categorical_21)))


ggplotly(q)


})



```

